### 2017-02-18 2017mergingmerges/section/XX-Processes.tex
Make map process creation combinato

>>>>

In terms of fusion, we could construct the result machine in multiple ways. One option is to perform the case branch first and then pull from @s2@. We could alternately pull from @s2@ first and then perform the case branch. By construction, the predicate used in the branch only refers to variables local to the @group@ machine, and the pull instruction from @B1@ stores its result in a variable local to the @merge@ machine. As the set of variables to not overlap then either ordering is correct. For this example we choose to perform the branch first, though will discuss the ramifications of this choice further in \TODO{ref}.
